Assessing the Added Predictive Power of Google's Community Mobility Report for COVID-19 Forecasting on a County-Level

### 2025-04-21 code/analysis-code/statisitical-analysis.qmd
Meta data

```
```{r}
# plot baseline lasso model prediction vs actual
plot_base_lasso <- base_final_lasso_test_results %>%
  ggplot(aes(x = new_cases, y = predicted)) +
  geom_point(alpha = 0.6, color = "darkgreen") +
  geom_abline(slope = 1, intercept = 0, color = "red", linetype = "dashed") +
  labs(
    title = "Base Lasso",
    x = "Actual Cases", y = "Predicted Cases"
  ) +
  theme_bw()

>>>>

```{r}
# plot baseline lasso model prediction vs actual
plot_base_lasso <- base_final_lasso_test_results %>%
  ggplot(aes(x = new_cases, y = predicted)) +
  geom_point(alpha = 0.6, color = "darkgreen") +
  geom_abline(slope = 1, intercept = 0, color = "red", linetype = "dashed") +
  labs(
    title = "Base Lasso",
    x = "Actual Cases", y = "Predicted Cases"
  ) +
  theme_bw()

### 2025-04-21 products/manuscript/Manuscript.qmd
Meta data

The analysis was conducted on RStudio 4.3.2 on Windows 11. The following R packages were used: ggplot2 [@wickhamGgplot2CreateElegant2019], broom [@robinsonBroomConvertStatistical2022], here [@mullerHereSimplerWay2020], glmnet [@friedmanGlmnetLassoElasticNet2021], MASS [@ripleyMASSSupportFunctions2022], tidymodels [@kuhnTidymodelsEasilyInstall2023], dplyr [@wickhamDplyrGrammarData2020], rsample [@frickRsampleGeneralResampling2025], parsnip [@kuhnParsnipCommonAPI2025], future [@bengtssonFutureUnifiedParallel2025], vip [@greenwellVipVariableImportance2023], zoo [@zeileisZooS3Infrastructure2021], patchwork [@pedersenPatchworkComposerPlots2020], e1071 [@meyerE1071MiscFunctions2022], scales [@wickhamScalesScaleFunctions2022], RColorBrewer [@neuwirthRColorBrewerColorBrewerPalettes2022], corrplot [@weiCorrplotVisualizationCorrelation2017], reshape2 [@wickhamReshape2FlexiblyReshape2020], tidyr [@wickhamTidyrTidyMessy2020], lubridate [@spinuLubridateMakeDealing2022], readxl [@wickhamReadxlReadExcel2019], stringr [@wickhamStringrSimpleConsistent2019], skimr [@waringSkimrCompactFlexible2022], tigris [@walkerTigrisLoadCensus2025], and sf [@pebesmaSfSimpleFeatures2021]

>>>>

The analysis was conducted on RStudio 4.3.2 on Windows 11. The following R packages were used: ggplot2 [@wickhamGgplot2CreateElegant2019], broom [@robinsonBroomConvertStatistical2022], here [@mullerHereSimplerWay2020], glmnet [@friedmanGlmnetLassoElasticNet2021], MASS [@ripleyMASSSupportFunctions2022], tidymodels [@kuhnTidymodelsEasilyInstall2023], dplyr [@wickhamDplyrGrammarData2020], rsample [@frickRsampleGeneralResampling2025], parsnip [@kuhnParsnipCommonAPI2025], future [@bengtssonFutureUnifiedParallel2025], vip [@greenwellVipVariableImportance2023], zoo [@zeileisZooS3Infrastructure2021], patchwork [@pedersenPatchworkComposerPlots2020], e1071 [@meyerE1071MiscFunctions2022], scales [@wickhamScalesScaleFunctions2022], RColorBrewer [@neuwirthRColorBrewerColorBrewerPalettes2022], corrplot [@weiCorrplotVisualizationCorrelation2017], reshape2 [@wickhamReshape2FlexiblyReshape2020], tidyr [@wickhamTidyrTidyMessy2020], lubridate [@spinuLubridateMakeDealing2022], readxl [@wickhamReadxlReadExcel2019], stringr [@wickhamStringrSimpleConsistent2019], skimr [@waringSkimrCompactFlexible2022], gtExtras [@mockGtExtrasExtendingGt2023], webshot2[@changWebshot2TakeScreenshots2023], tigris [@walkerTigrisLoadCensus2025], and sf [@pebesmaSfSimpleFeatures2021]
